Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-01-15 TEBenchmarkPaper/article.tex
Remove out-of-context remarks

% 1. history of terminology
FIXME Automated theory formation, the focus of this paper, derives its
terminology from psychology in which the term ``concept formation'' is
used (see, for example, \cite{bruner:67}) to describe the search for
features which differentiate exemplars from non-exemplars of various
categories. Lenat used this term in his 1977 paper: {\em Automated
  Theory Formation in Mathematics} \cite{lenat:77} and we have
extended it to describe a family of techniques used to construct and
evaluate concepts, conjectures, examples and proofs (embodied in the
HR, HRL and GC systems and derivatives, as described above).

>>>>

% 1. history of terminology
Automated theory formation derives its terminology from psychology in which the
term ``concept formation'' is used (see, for example, \cite{bruner:67}) to
describe the search for features which differentiate exemplars from
non-exemplars of various categories. Lenat used this term in his 1977 paper:
{\em Automated Theory Formation in Mathematics} \cite{lenat:77}.
